---
title: "Descriptive_Data_Analysis_with_mtcars"
author: "Arif_Furkan"
date: "2024-06-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Before you start; “Zorunlu Paket Yükleniyor” means Installing required package

# Data Loading and Preprocessing

```{r}
require(dplyr)
require(ggplot2)
require(GGally)
data(mtcars)
```

# Data Visualization

```{r}
mtcars %>%
select(mpg, disp, cyl, hp) %>%
ggpairs(.)
```

# Installing and Using Other Packages

```{r}
require(gcookbook)
require(corrplot)
mcor <- cor(mtcars)
corrplot(mcor)
```

# Other Analytics and Visualizations
## Graphs are created with the qgraph package.
## Multivariate analyzes are performed with the MVA package.

```{r}
require(qgraph)
require(corrplot)
qgraph(mcor,layout = "spring")
require(MVA)
install.packages("MVA")
with(mtcars, chiplot(mpg,hp))
stem(mtcars$hp)
```

## Operations are performed on outliers with the OutliersO3 package.

```{r}
require(OutliersO3)
data("stackloss")
outdata <- O3prep(stackloss,method =c("HDo", "BAC", "DDC"), tols=0.05)
outmulti <- O3plotM(outdata)
outmulti$nOut
outmulti$gO3
```

## Crosstabs are created with the gmodels package.

```{r}
require(gmodels)
CrossTable(mtcars$vs,mtcars$gear,prop.t=TRUE, prop.r=TRUE, prop.c=TRUE,
expected=FALSE,chisq=FALSE, format="SPSS")
```

## Data analysis and summarization processes are performed with packages such as DescTools and dataMaid.

```{r}
require(readr)
require(DescTools)
Desc(mtcars$mpg, plotit = TRUE, main= "MPG Data")
Desc(as.factor(mtcars$gear), plotit=FALSE, main ="Gear Variable")
Desc(as.factor(gear)~mpg, data = mtcars, plotit = FALSE,
main = "Gear ve Mpg Data")
```
```{r}
require(dataMaid)
dataMaid::summarize(mtcars["mpg"], reportstyleOutput = TRUE)
```
