---
title: "Port_Freight_Traffic"
author: "Arif_Furkan"
date: "2024-06-29"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Before you start; "Zorunlu Paket Yükleniyor" means Installing required package

# Loading Port Data
### This data consists of a list ranking the busiest ports from 2004 to 2014.
```{r}
require(dplyr)
url.world_ports <-
url("http://sharpsightlabs.com/wp-content/datasets/world_ports.RData")
load(url.world_ports)
glimpse(df.world_ports)
```

# Creating a Theme
```{r}
require(ggplot2)
theme.porttheme <-
theme(text = element_text(color = "#444444")) +
theme(plot.title = element_text(size = 18)) +
theme(plot.subtitle = element_text(size = 16)) +
theme(axis.title = element_text(size = 14)) +
theme(axis.title.y = element_text(angle = 0, vjust = .5,
margin = margin(r = 15))) +
theme(axis.text = element_text(size = 10)) +
theme(axis.title.x = element_text(margin = margin(t = 20))) +
theme(legend.title = element_blank())
```

# Chart of the 25 Busiest Ports by Volume
```{r}
df.world_ports %>%
filter(year == 2014, rank <= 25) %>%
ggplot(aes(x = reorder(port, volume), y = volume)) +
geom_bar(stat = "identity", fill = "dark red") +
geom_text(aes(label = volume), hjust = 1.1, color = "#FFFFFF") +
scale_y_continuous(labels = scales::comma_format()) +
coord_flip() +
labs(title = "25 Busiest Ports") +
labs(x="", y = "Shipment Volume (1000 TEUs)") +
theme.porttheme
```

### From this chart we can clearly see that the busiest ports are in the Far East - China region.

# Development of ports by years 
```{r}
param.rank_n = 15
df.world_ports %>%
filter(rank <= param.rank_n) %>%
mutate(china_flag = ifelse(economy == "China", T,F)) %>%
mutate(china_labels = ifelse(china_flag == T, port,"other")) %>%
ggplot(aes(x = year, y = rank, group = port_label)) +
geom_line(aes(color = china_labels, alpha = china_flag), size = 2) +
geom_point(aes(color = china_labels, alpha = china_flag), size = 2.3) +
geom_point(color = "#FFFFFF", alpha = .8, size = .3) +
geom_text(data = df.world_ports %>%
filter(year == "2014", rank <= param.rank_n),
aes(label = port_label, x = '2014') , hjust = -.05,
color = "#888888",
size = 4) +
geom_text(data = df.world_ports %>%
filter(year == "2004", rank <= param.rank_n),
aes(label = port_label, x = '2004') , hjust = 1.05,
color = "#888888",
size = 4) +
scale_x_discrete(expand = c(.3, .3)) +
scale_y_reverse(breaks = c(1,5,10,15)) +
scale_alpha_discrete(range = c(.4,.9)) +
labs(x = "Year", y = "Row") +
theme.porttheme +
theme(panel.grid.major.x = element_line(color = "#F3F3F3")) +
theme(panel.grid.major.y = element_blank()) +
theme(panel.grid.minor = element_blank()) +
theme(legend.position = "none") +
theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
scale_color_manual(values = c("#4e79a5","#f18f3b","#af7a0a","#e0585b","#5aa155","#edc958","#77b7b2","#BBBBBB"))
```

### In this chart, we see the density ranking of ports by year. In this chart the colored lines indicate Chinese ports. As we can see from the graph, we can say that Chinese ports have made great progress since the early 2000s.

# Preparing the Map Theme
```{r}
theme.maptheeme <-
theme(text = element_text(color = "#444444")) +
theme(plot.title = element_text(size = 30)) +
theme(panel.background = element_rect(fill = "#FCFCFF")) +
theme(plot.subtitle = element_text(size = 18)) +
theme(panel.grid = element_blank()) +
theme(axis.text = element_blank()) +
theme(axis.ticks = element_blank()) +
theme(axis.title = element_blank()) +
theme(legend.position = c(.17,.35)) +
theme(legend.background = element_blank()) +
theme(legend.key = element_blank()) +
theme(legend.title = element_text(size = 16)) +
theme(legend.text = element_text(size = 10))
```

# Preparation of Graphics to Show Ports on the Map
```{r}
require(tidyverse)
map.world_polygon <- map_data("world")
df.world_ports %>%
filter(year == "2014") %>%
ggplot(aes(x = lon, y = lat)) +
geom_polygon(data = map.world_polygon, aes(x = long, y = lat,
group = group),
fill = "#AAAAAA",colour = "#818181", size = .15) +
geom_point(aes(size = volume), color = "#DD0000", alpha = .15) +
geom_point(aes(size = volume), color = "#DD0000", alpha = .7,
shape = 1) +
scale_size_continuous(range = c(.2,10), breaks = c(5000, 10000, 30000),
name = "Volume\n(1000 TEU)") +
theme.maptheeme
```

### This chart shows the port density map for 2014. Ports are shown with red dots. Ports have larger circles in proportion to their density. Here we can see how busy the Far Eastern ports are.

