---
title: "ANOVA_Example"
author: "Arif_Furkan"
date: "2024-06-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries and Data

```{r}
require(ggplot2)
data(diamonds)
```

# Creating a Boxplot

```{r, fig.width=7, fig.height=4}
ggplot(data = diamonds) + geom_boxplot(aes(cut,price))+
theme_bw() + xlab("Cut") + ylab("Price") 
```

# One-Way ANOVA

```{r}
anova.1 <- aov(price~cut, data = diamonds)
summary(anova.1)
print(anova.1)
```

# Fitting a Linear Model

```{r}
fit <- lm(price~cut, data = diamonds)
anova.2 <- anova(fit)
anova.2
```

# Another ANOVA using the car package

```{r}
require(car)
fit <- lm(price ~ cut, data = diamonds)
anova.3 <- Anova(fit)
require(car)
anova.3 <- Anova(fit)
anova.3
```

# Pairwise T-Tests

### Performs pairwise t-tests to compare the means of diamond prices between different cuts.

```{r}
pairwise.t.test(diamonds$price, diamonds$cut, p.adjust.method = "bonferroni")
```

### From the results, it can be seen that the Fair-Premium and Good-Very Good groups are not statistically different from each other, but there is a statistically significant difference in the others.

# Tukey's Honest Significant Difference Test

```{r}
TukeyHSD(anova.1, ordered = FALSE)
```

### As can be seen, consistent with the above result, there is no statistically significant difference between Fai -Premium and Good-Very Good, but there is a difference between the other groups.

# Two-Way ANOVA

```{r}
fit.2 <- lm(price ~ cut*color, data = diamonds)
library(car)
anova.4 <- Anova(fit.2, type = "III")
anova.4
```

# Interaction Plot

```{r}
with(diamonds,{
interaction.plot(cut, color, price, col = c(1:4))})
```

### While the price change is the same in most colors, there is no price decrease in the good cuts in Colors I and G. Apart from this, the price change generally occurs in the same way.
