---
title: "Evaluation of Variables with Hypothesis Tests"
author: "Arif_Furkan"
date: "2024-06-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Before you start; "Zorunlu Paket Yükleniyor" means Installing required package

# Motor Cars (mtcars) Dataset Analysis

```{r}
data(mtcars)
summary(mtcars$mpg)
t.test(mtcars$mpg, mu = 25, altenative = "two.sided")
```

## Attention should be paid to the assumption of whether the variances are equal (var.equal)

# Diamond Prices Example

```{r}
require(knitr)
require(dplyr)
require(ggplot2)
data(diamonds)
force(diamonds)
head(diamonds,3)
fair <- diamonds %>%
filter(cut == "Fair") %>%
select(price)
premium <- diamonds %>%
filter(cut == "Premium") %>%
select(price)
t.test(fair$price, premium$price, var.equal = FALSE)
```

## As seen in the results, the p-value is 0.019 and "Fair" and "premium" at a 5% significance level. The null hypothesis that the average prices of diamonds with different cuts are equal is rejected.

# Wilcoxon Test

```{r}
require(UsingR)
data(exec.pay)
summary(exec.pay)
wilcox.test(exec.pay, conf.int = TRUE)
```

## As seen from the test results, the 95% confidence interval is between 25-32 thousand dollars.

# Prop Test

```{r}
prop.test(x = c(40,320), n = c(220,775), alternative = "two.sided")
```

## It tests whether the rates between two groups are equal. x is the number of successes, n is the total sample size.


# Participation in Education (Quine) Example

```{r}
library(MASS)
data(quine)
head(quine)
attach(quine)
tab <- table(Eth,Sex)
prop.test(tab, alternative = "two.sided", conf.level = 0.95,
correct = FALSE)
```
## When we look at the results in question, the null hypothesis is rejected because the p-value is very high, such as 0.94.

# Seat Belt Example

```{r}
crash <- matrix(c(178,144,135,47), ncol=2)
colnames(crash) <- c('Alive','Death')
rownames(crash) <- c('Without_Belt','Belted')
prop.table(crash)
prop.test(crash)
```

## With these results, the null hypothesis that the death rates of seat belt users and non-users are not different is rejected.

# Chi-Square Test (Relationship between Hepatitis and Tattoos)

## Let's say the results obtained in a study on the relationship between hepatitis disease and the place where tattoos are made (licensed, unlicensed and not tattooed) are as follows:

```{r}
hep <- matrix(c(17,35,8,53,22,491), ncol = 2)
colnames(hep) <- c('Positive','Negative')
rownames(hep) <- c('Licensed','Unlicensed','Not_Tattooed')
prop.table(hep)
chisq.test(hep)
```
## According to the test results obtained, the null hypothesis that there is no relationship between tattooing and hepatitis disease is rejected at the 5% significance level.
