---
title: "Distributions"
author: "Arif_Furkan"
date: "2024-06-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functions for distributions
### In this project, we see how statistical distributions are implemented in R and finally we apply the central limit theorem.

# Uniform Distribution

```{r}
x<-dunif(0.5, min = 0, max = 1)
dunif(x, min = 0, max = 1, log = FALSE)
q<-punif(0.5, min = 0, max = 1)
punif(q, min = 0, max = 1, lower.tail = TRUE, log.p = FALSE)
p<-qunif(0.5, min = 0, max = 1)
qunif(p, min = 0, max = 1, lower.tail = TRUE, log.p = FALSE)
n<-runif(10, min = 0, max = 1)
runif(n, min = 0, max = 1)
```

# Binomial Distribution

These probability and size values were chosen randomly.

```{r}
size<-5
prob<-0.5
dbinom(x, size, prob, log = FALSE)
pbinom(q, size, prob, lower.tail = TRUE, log.p = FALSE)
qbinom(p, size, prob, lower.tail = TRUE, log.p = FALSE)
rbinom(n, size, prob)
```
# Normal Distribution

This mean value was chosen randomly.

```{r}
mean<-0
dnorm(x, mean = 0, sd = 1, log = FALSE)
pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
qnorm(p, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
rnorm(n, mean = 0, sd = 1)
```
# Hypergeometric Distribution

These m, k and e values were chosen randomly.

```{r}
m<-10
k<-7
e<-5
dhyper(x, m, e, k, log = FALSE)
phyper(q, m, e, k, lower.tail = TRUE, log.p = FALSE)
qhyper(p, m, e, k, lower.tail = TRUE, log.p = FALSE)
rhyper(n, m, e, k)
```
# Poisson Distribution

This lambda value was chosen randomly.

```{r}
lambda<-2
dpois(x, lambda, log = FALSE)
ppois(q, lambda, lower.tail = TRUE, log.p = FALSE)
qpois(p, lambda, lower.tail = TRUE, log.p = FALSE)
rpois(n, lambda)
```
# Geometric Distribution

```{r}
dgeom(x, prob, log = FALSE)
pgeom(q, prob, lower.tail = TRUE, log.p = FALSE)
qgeom(p, prob, lower.tail = TRUE, log.p = FALSE)
rgeom(n, prob)
```
# Central Limit Theorem
## Load necessary packages

```{r}
require(ggplot2)
```
## Create a population from a Poisson distribution
```{r}
lambda <- 5  # Parameter for Poisson distribution (mean)
population <- rpois(10000, lambda)  # Population data
```
## Sample size and number of simulations
```{r}
n <- 30  # Sample size
num_simulations <- 1000  # Number of simulations
```
## Calculate the sample means
```{r}
sample_means <- replicate(num_simulations, {
sample <- sample(population, n, replace = TRUE)
mean(sample)})
```
## Save the sample means as a data frame
```{r}
sample_means_df <- data.frame(sample_means)
```
## Plot the histogram of sample means
```{r}
ggplot(sample_means_df, aes(x = sample_means)) +
geom_histogram(aes(y = ..density..), bins = 30, fill = "blue", color = "black", alpha = 0.7) +
stat_function(fun = dnorm, args = list(mean = mean(sample_means), sd = sd(sample_means)), color = "red", size = 1) +
labs(title = "Central Limit Theorem Example",
x = "Sample Means",
y = "Density") +
theme_minimal()
```

### This example demonstrates the Central Limit Theorem, showing how the distribution of sample means approaches a normal distribution as the sample size increases.